*Prochlorococcus marinus* responses to light and oxygen

### 2024-03-14 Code/Manuscript_O2.Rmd
Added Mireille as receiving NBIF grant

To Be Entered through PLoSONe system and deleted here Czech Academy of
Science (OP) visiting fellowship supporting DAC work at AlgaTech Canada
Research Chair in Phytoplankton Ecophysiology (DAC) Natural Sciences and
Engineering Research Council of Canada, 'Latitude and Light' (DAC)
Canada Foundation for Innovation (DAC) New Brunswick Foundation for
Innovation (DAC) Rice Graduate Fellowship 2021 and 2022 (MS)

>>>>

To Be Entered through PLoSONe system and deleted here Czech Academy of
Science (OP) visiting fellowship supporting DAC work at AlgaTech Canada
Research Chair in Phytoplankton Ecophysiology (DAC) Natural Sciences and
Engineering Research Council of Canada, 'Latitude and Light' (DAC)
Canada Foundation for Innovation (DAC) New Brunswick Foundation for
Innovation (DAC and MS) Rice Graduate Fellowship 2021 and 2022 (MS)
